Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-30 manuscript/supplemental_material.Rnw
make the figure more squat

\begin{figure}[tbh]
<<core.placenta.transcriptome.housekeeping,fig.width=5,fig.height=10,out.height="0.8\\textheight",echo=FALSE>>=
cptlh <-
    core.placenta.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                            Species) & housekeeping==TRUE,]
cptlh <- cptlh[,Species:=factor(gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",capfirst(Species)),
                              levels=gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",
                                          capfirst(names(species.names))))]

print(ggplot(cptlh,aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10(labels=trans_format("log10", math_format(10^.x)))+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual("Species",
                         guide=guide_legend(#nrow=1,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9),
                                            title.position="top"
                                            ),
                         values=0:18)+
      # scale_color_discrete(NULL)+
      coord_flip()+
      xlab("Human Ortholog Name")+
      ylab("Gene Expression (FPKM)")+
      theme_bw() +
      theme(legend.position=c(0.7,0.15),
            axis.text.y=element_text(face="italic",size=5),
            legend.margin=unit(0,"mm"),
            legend.justification="left",
            plot.margin=unit(c(0,0,0,0),"mm")
            ))
@ 
\caption{Housekeeping genes excluded from the Core Placenta Transcriptome.
  \Sexpr{cptlh[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed ($\mathrm{FPKM} \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied which are housekeeping genes~%
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited}
  ordered (from top to bottom) by median expression.}
\label{fig:core_placenta_transcriptome_housekeeping}
\end{figure}

>>>>

\begin{figure}[tbh]
<<core.placenta.transcriptome.housekeeping,fig.width=6,fig.height=8,out.height="0.8\\textheight",echo=FALSE>>=
cptlh <-
    core.placenta.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                            Species) & housekeeping==TRUE,]
cptlh <- cptlh[,Species:=factor(gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",capfirst(Species)),
                              levels=gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",
                                          capfirst(names(species.names))))]

print(ggplot(cptlh[FPKM > 0.9,],aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10(labels=trans_format("log10", math_format(10^.x)))+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual("Species",
                         guide=guide_legend(#nrow=1,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9),
                                            title.position="top"
                                            ),
                         values=0:18)+
      # scale_color_discrete(NULL)+
      coord_flip()+
      xlab("Human Ortholog Name")+
      ylab("Gene Expression (FPKM)")+
      theme_bw() +
      theme(legend.position=c(0.7,0.15),
            axis.text.y=element_text(face="italic",size=5),
            legend.margin=unit(0,"mm"),
            legend.justification="left",
            plot.margin=unit(c(0,0,0,0),"mm")
            ))
@ 
\caption{Housekeeping genes excluded from the Core Placenta Transcriptome.
  \Sexpr{cptlh[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed ($\mathrm{FPKM} \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied which are housekeeping genes~%
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited}
  ordered (from top to bottom) by median expression.}
\label{fig:core_placenta_transcriptome_housekeeping}
\end{figure}
